---
title: "pepannot_guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{pepannot_guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Introduction to pepannot

Welcome to the pepannot package vignette! This vignette provides a brief overview of how to use the pepannot package for annotating peptide sequences. 

## What is pepannot?

The pepannot package is use for annotating peptide sequences with various modifications. It allows you to easily add annotations such as [+80] for phosphorylation and [+16] for oxidation to peptide sequences, enhancing your ability to recognize which residues were modified.


```{r setup}
# Loading the pepannot package
library(pepannot)
```

```{r}
# Loading additional required packages
library(readr)
library(dplyr)
```


```{r}
# Read the CSV file containing peptide data
b <- readr::read_csv(system.file("extdata", "anon.csv", package = "pepannot"))
```

```{r}
# Annotate peptide sequences with modifications
c <- b |>
  dplyr::rowwise() |>
  dplyr::mutate(new_column_name = annotate_positions(seq, residue_posn)) |>
  dplyr::mutate(another_column_name = annot_sequence(seq, residue_posn, pattern))
```

